A Horrocks-type theorem for even orthogonal $K_2$

### 2020-06-30 horrocks.tex
Convert bibliography to the thebibliography format

%
%-----------------headlines-----------------------------------
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[breaklinks=false,unicode]{hyperref}
\definecolor{DarkPurple}{rgb}{0.40,0.0,0.20}
\hypersetup{colorlinks=true,citecolor=NavyBlue,linkcolor=DarkPurple,urlcolor=NavyBlue}
\usepackage{color} 
%\usepackage[breaklinks=false,unicode]{hyperref}
\usepackage[backend=biber, bibencoding=utf8, giveninits=true, citestyle=numeric-comp, sortlocale=en_US, url=false, doi=false, eprint=true, maxbibnames=4]{biblatex}
\usepackage[capitalize]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage{tikz}
\usepackage{enumitem}
\usepackage{filecontents}

@@

\def\LOCAL{\horrocks.files}

\addbibresource{horrocks.bib}
\renewbibmacro*{volume+number+eid}{\ifentrytype{article}{\- \iffieldundef{volume}{}{Vol.~\printfield{volume},}\iffieldundef{number}{}{ No.~\printfield{number},}}}
\renewbibmacro{in:}{\ifentrytype{article}{}{\printtext{\bibstring{in}\intitlepunct}}}
\newbibmacro{string+doi}[1]{\iffieldundef{doi}{\iffieldundef{url}{#1}{\href{\thefield{url}}{#1}}}{\href{https://dx.doi.org/\thefield{doi}}{#1}}}
\DeclareFieldFormat[article, inproceedings, inbook, book, online]{title}{\usebibmacro{string+doi}{\mkbibquote{#1}}}
\renewcommand*{\bibfont}{\footnotesize}
\defbibheading{bibliography}[\refname]{\section*{#1} \markboth{}{}}

@@

The following proposition is the main result of this subsection and also a direct generalization of~\cite[Lemma~3.3]{Tu83}.
\begin{prop} \label{lemma33} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the homomorphism $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$, induced by the natural embedding of generators, is an isomorphism. In particular, the obvious homomorphism $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism. \end{prop}
\begin{proof}
 We need to construct a homomorphism $j_n$ which would be the inverse of $i_n$. 
 We start with a homomorphism $\widetilde{j}_n^\Phi \colon F\langle \mathcal{X}^\Phi_{\leq n+1} \rangle \to \St^{\leq n}(\Phi, B)$ defined via
 \[ \widetilde{j}^{\Phi}_n(x_\alpha(at^k)) = \begin{cases} x_\alpha(at^k), & k\leq n; \\
      [x_{\alpha - \beta} (N_{\alpha-\beta, \beta} \cdot at^{k-1}), x_{\beta}(t)], & k = n+1, \end{cases} \]
 where $\beta$ is any root of $\Phi$ forming a sharp angle with $\alpha$.
 A standard argument, cf. \cite[Proposition~1.1]{Re75} or~\cite[Proposition~3.2.2]{RS76}, shows that $\widetilde{j}^\Phi_n$ does not depend on the choice of $\beta$.

@@

\printbibliography
\Addresses
\begin{filecontents}{horrocks.bib}
@Article{Abe83,
    Author    = {Abe, Eiichi},
    Title     = {Whitehead groups of {C}hevalley groups over polynomial rings},    
    Journal   = {Comm. Alg.},    
    Number    = 12,
    Volume    = 11,
    Pages     = {1271--1307},
    Year      = 1983,    
    Doi       = {10.1080/00927878308822906}}

@Article{A13,
    Author    = {Allcock, Daniel},
    Title     = {Steinberg groups as amalgams},
    Journal   = {Alg. Number Th.},    
    Volume    = 10,
    Number    = 8,
    Pages     = {1791--1843},
    Year      = 2016,
    Doi       = {10.2140/ant.2016.10.1791}}

@Article{AF17,
    Author    = {Asok, Aravind and Fasel, Jean},
    Title     = {An explicit KO-degree map and applications},    
    Journal   = {J. Top.},
    Volume    = 10,
    Issue     = 1,
    Pages     = {268--300},
    Year      = 2017,    
    Doi       = {10.1112/topo.12007}}

@Article{Ba74,
    Author    = {Bass, Hyman},
    Title     = {Clifford algebras and spinor norms over a commutative ring},    
    Journal   = {Amer. J. Math.},
    Volume    = 96,
    Number    = 1,
    Pages     = {156--206},
    Year      = 1974,
    Doi       = {10.2307/2373586}}

@Book{Bou81,
    Author    = {Bourbaki, Nicolas},
    Title     = {Groupes et algèbres de Lie: Chapitres 4, 5 et 6},
    Publisher = {Masson},
    Year      = 1981}

@Inproceedings{DS73,
    Author    = {Dennis, R. Keith and Stein, Michael R.},
    Title     = {The functor $K_2$: A survey of computations and problems},    
    Booktitle = {Classical Algebraic K-Theory, and Connections with Arithmetic},
    Publisher = {Springer},
    Pages     = {241--303},
    Year      = 1973,
    Doi       = {10.1007/BFb0073728}}

@Article{FRS12,
    Author    = {Fasel, Jean and Rao, Ravi and Swan, Richard},
    Title     = {On stably free modules over affine algebras},
    Journal   = {Publ. Math. IH{\'E}S},
    Volume    = 116,
    Issue     = 1,
    Pages     = {223--243},
    Year      = 2012,
    Doi       = {10.1007/s10240-012-0041-y}}

@Article{Ho05,
    Author    = {Hornbostel, Jens},
    Title     = {$\mathbb{A}^1$-representability of Hermitian K-theory and Witt groups},    
    Journal   = {J. Top.},
    Volume    = 44,
    Number    = 3,
    Pages     = {661--687},
    Year      = 2005,
    Doi       = {10.1016/j.top.2004.10.004}}

@Article{Ho64,
    Author    = {Horrocks, Geoffrey},
    Title     = {Projective modules over an extension of a local ring},    
    Journal   = {Proc. London Math. Soc.},
    Volume    = 3,
    Number    = 4,
    Pages     = {714--718},
    Year      = 1964,
    Doi       = {10.1112/plms/s3-14.4.714}}

@Article{Hur77,
    Author    = {Hurrelbrink, J{\"u}rgen},
    Title     = {Endlich pr\"asentierte arithmetische Gruppen und $K_{2}$ {\"u}ber Laurent-Polynomringen},
    Journal   = {Math. Ann.},
    Volume    = 225,    
    Number    = 2,
    Pages     = {123--129},
    Year      = 1977,
    Doi       = {10.1007/BF01351716}}

@Article{Ka80,
    Author    = {Karoubi, Max},
    Title     = {Le th{\'e}oreme fondamental de la K-th{\'e}orie hermitienne},    
    Journal   = {Ann. Math.},
    Volume    = 112,
    Number    = 2,
    Pages     = {259--282},
    Year      = 1980,
    Doi       = {10.2307/1971147}}

@Book{Lam10,
    Title     = {Serre's problem on projective modules},
    Author    = {Lam, Tsit-Yuen},
    Publisher = {Springer Science \& Business Media},
    Year      = {2010},
    Doi       = {10.1007/978-3-540-34575-6}}

@Article{LS17,
    Author    = {Lavrenov, Andrei and Sinchuk, Sergey},
    Title     = {Centrality of odd orthogonal $K_2$},    
    Journal   = {J. Pure Appl. Alg.},
    Volume    = 221,
    Pages     = {1134--1145},
    Year      = 2017,    
    Url       = {https://arxiv.org/pdf/1606.00272.pdf}}

@Article{La18,
    Author    = {Lavrenov, Andrei},
    Title     = {A local-global principle for symplectic $K_2$},    
    Journal   = {Doc. Math.},    
    Volume    = 23,
    Pages     = {653--675},
    Year      = 2018,
    Doi       = {10.25537/dm.2018v23.653-675}}

@Article{Lo78,
    Author    = {Loday, Jean-Louis},
    Title     = {Cohomologie et groupes de Steinberg relatifs},
    Journal   = {J. Alg.},    
    Volume    = 54,
    Number    = 1,
    Pages     = {178--202},
    Year      = 1978,
    Doi       = {10.1016/0021-8693(78)90025-X}}

@Article{Ma69,
    Author    = {Matsumoto, Hideya},
    Title     = {Sur les sous-groupes arithm{\'e}tiques des groupes semi-simple d{\'e}ploy{\'e}s},    
    Journal   = {Ann. Sci. ENS},
    Volume    = 2,
    Number    = 1,
    Pages     = {1--62},
    Year      = 1969,
    Url       = {http://eudml.org/doc/81843}}

@Article{Mo04,
    Author    = {Morel, Fabien},
    Title     = {Sur les puissances de l'id{\'e}al fondamental de l'anneau de Witt},    
    Journal   = {Comm. Math. Helv.},
    Volume    = 79,
    Number    = 4,
    Pages     = {689--703},
    Year      = 2004,
    Doi       = {10.1007/s00014-004-0815-z}}

@Article{MR91,
    Author    = {Morita, Jun and Rehmann, Ulf},
    Title     = {Symplectic $K_2$ of Laurent polynomials, associated Kac--Moody groups and Witt rings},    
    Journal   = {Math. Z.},
    Volume    = 206,
    Number    = 1,
    Pages     = {57--66},
    Year      = 1991,
    Doi       = {10.1007/BF02571324}}

@Article{Pa89,
    Author    = {Panin, Ivan},
    Title     = {On stabilization for orthogonal and symplectic algebraic K-theory (Russian)},
    Journal   = {Leningrad Math. J.},    
    Volume    = 1,
    Number    = 3,
    Pages     = {741--754},
    Year      = 1990,
    Url       = {http://www.mathnet.ru/links/a46c953dc23ca4b3c44578c283cd59c8/aa27.pdf}}

@Article{Qu76,
    Author    = {Quillen, Daniel},
    Title     = {Projective modules over polynomial rings},
    Journal   = {Inv. Math.},    
    Volume    = 36,
    Number    = 1,
    Pages     = {167--171},
    Year      = 1976,
    Doi       = {10.1007/BF01390008}}

@Article{Re75,
    Author    = {Rehmann, Ulf},
    Title     = {Pr{\"a}sentationen von Chevalleygruppen {\"u}ber $k[t]$},    
    Year      = {1975},
    Url       = {http://www.math.uni-bielefeld.de/~rehmann/Publ/praesentation.pdf}}

@Inproceedings{RS76,
    Author    = {Rehmann, Ulf and Soul{\'e} , Christophe},
    Title     = {Finitely presented groups of matrices},    
    Booktitle = {Algebraic K-Theory},
    Publisher = {Springer},        
    Series    = {Lect. Notes. Math.},
    Volume    = 551,
    Pages     = {164--169},
    Year      = 1976,
    Doi       = {10.1007/BFb0079999}}

@Article{Sch16,
    Author    = {Schlichting, Marco},
    Title     = {Hermitian K-theory, derived equivalences and Karoubi's fundamental theorem},
    Journal   = {J. Pure Appl. Alg.},    
    Volume    = 221,
    Issue     = 7,
    Pages     = {1729--1844},
    Year      = 2017,
    Doi       = {10.1016/j.jpaa.2016.12.026}}

@Article{S15,
    Author    = {Sinchuk, Sergey},
    Title     = {On centrality of $K_2$ for {C}hevalley groups of type $\mathsf{E}_\ell$ },    
    Journal   = {J. Pure Appl. Alg.},
    Volume    = 220,    
    Number    = 2,    
    Pages     = {857--875},
    Year      = 2016,
    Doi       = {10.1016/j.jpaa.2015.08.003}}

@Article{St-Ded,
    Author    = {Stavrova, Anastasia},
    Title     = {Chevalley groups of polynomial rings over Dedekind domains},
    Journal   = {J. Gr. Th.},
    Volume    = 23,
    Issue     = 1,
    Pages     = {121--132},
    Year      = 2020,
    Doi       = {10.1515/jgth-2019-0100}}

@Article{St-poly,
    Author    = {Stavrova, Anastasia},
    Title     = {Homotopy invariance of non-stable $K_1$-functors},    
    Journal   = {J. K-th.},
    Volume    = 13,
    Number    = 2,
    Pages     = {199--248},   
    Year      = 2014,
    Doi       = {10.1017/is013006012jkt232}}

@Article{St78,
    Author    = {Stein, Michael R.},
    Title     = {Stability theorems for $K_1$, $K_2$ and related functors modeled on Chevalley groups},    
    Journal   = {Japan J. Math.},
    Volume    = 4,
    Issue     = 1,
    Pages     = {77--108},
    Year      = 1978,
    Doi       = {10.4099/math1924.4.77}}

@Article{St71,
    Author    = {Stein, Michael R},
    Title     = {Generators, relations and coverings of Chevalley groups over commutative rings},
    Journal   = {Amer. J. Math.},
    Volume    = 93,
    Number    = 4,
    Pages     = {965--1004},
    Year      = 1971,
    Doi       = {10.2307/2373742}}

@Article{Ste73,
    Author    = {Stein, Michael R.},
    Title     = {Surjective stability in dimension 0 for $K_2$ and related functors},    
    Journal   = {Trans. Amer. Math. Soc.},
    Volume    = 178,
    Pages     = {165--191},
    Year      = 1973,
    Doi       = {10.2307/1996696}}

@Book{St67,
    Author    = {Steinberg, Robert and Faulkner, John and Wilson, Robert},
    Title     = {Lectures on Chevalley groups},        
    Publisher = {Yale Univ. New Haven},
    Year      = 1967}

@Article{Su77,
    Author    = {Suslin, Andrei},
    Title     = {On the structure of the special linear group over commutative rings},    
    Journal   = {Math. USSR Izv.},        
    Volume    = 11,
    Pages     = {221--238},
    Year      = 1977,
    Doi       = {10.1070/IM1977v011n02ABEH001709}}

@Article{Su76,
    Author    = {Suslin, Andrei},
    Title     = {Projective modules over polynomial rings are free},    
    Journal   = {Dokl. Akad. nauk SSSR},
    Volume    = 229,
    Pages     = {1063--1066},
    Year      = 1976,
    Url       = {http://www.mathnet.ru/links/1ebfa3efeb44dfd494087eaf83a34450/dan40545.pdf}}

@Article{Su82,
    Author    = {Suslin, Andrei and Kopeiko, Vyacheslav},
    Title     = {Quadratic modules and the orthogonal group over polynomial rings},    
    Journal   = {J. Soviet Math.},
    Volume    = 20,
    Number    = 6,
    Pages     = {2665--2691},
    Year      = 1982,
    Doi       = {10.1007/BF01681481}}

@Article{ST76,
    Author    = {Suslin, Andrei and Tulenbaev, Marat},
    Title     = {Stabilization theorem for the {M}ilnor $K_2$-functor},
    Journal   = {J. Soviet Math.},    
    Volume    = 17,
    Number    = 2,
    Pages     = {1804--1819},
    Year      = 1981,
    Doi       = {10.1007/BF01091768}}

@InProceedings{Ta86,
    Author    = {Taddei, Giovanni},
    Title     = {Normalit\'e des groupes \'el\'ementaires dans les groupes de {C}hevalley sur un anneau},    
    Booktitle = {Applications of algebraic $\K$-theory to algebraic geometry and number theory, Part II (Boulder, Colo., 1983)},
    Series    = {Contemp. Math},
    Volume    = 55,
    Pages     = {693--710},       
    Year      = 1986,
    Url       = {http://www.ams.org/books/conm/055.2/862660/conm862660.pdf}}

@Article{Tu83,
    Author    = {Tulenbaev, Marat},
    Title     = {The Steinberg group of a polynomial ring},    
    Journal   = {Math. USSR Sb.},        
    Volume    = 45,
    Pages     = {131--144},
    Year      = 1983,
    Doi       = {10.1070/SM1983v045n01ABEH002591}}

@Article{Va86,
    Author    = {Vaserstein, Leonid},
    Title     = {On normal subgroups of Chevalley groups over commutative rings},
    Journal   = {Tohoku Math. J.},
    Volume    = 38,
    Issue     = 2,
    Pages     = {219--230},
    Year      = 1986,
    Doi       = {10.2748/tmj/1178228489}}

@Article{V00,
    Author    = {Vavilov, Nikolai},
    Title     = {A third look at weight diagrams},    
    Journal   = {Rend. Sem. Mat. Univ. Padova},   
    Volume    = 104,
    Pages     = {201--250},    
    Year      = 2000,
    Url       = {http://eudml.org/doc/108535}}

@Article{VP,
    Author    = {Vavilov, Nikolai and Plotkin, Eugene},
    Title     = {Chevalley groups over commutative rings: I. Elementary calculations},
    Journal   = {Acta Appl. Math.},    
    Volume    = 45,
    Issue     = 1,
    Pages     = {73--113},
    Year      = {1996},       
    Doi       = {10.1007/BF00047884}}

@Article{VZ18,
    Author    = {Vavilov, Nikolai and Zhang, Zuhong},
    Title     = {Generation of relative commutator subgroups in Chevalley groups. II},    
    Journal   = {Proc. Edinburgh Math. Soc.},
    Volume    = 63,
    Number    = 2,
    Pages     = {497--511},
    Year      = 2020,
    Doi       = {10.1017/S0013091519000555}}

@Mastersthesis{Vo11,
    Author    = {V{\"o}lkel, Konrad},
    Title     = {\href{http://static.konradvoelkel.de/download/da-voelkel-20110809.pdf}{Matsumotos Satz und $\mathbb{A}^1$-Homotopietheorie}},
    School    = {Uni. Freiburg},
    Type      = {Diplomarbeit}
    Year      = 2011}

@Book{Kbook,
    Author    = {Weibel, Charles A},
    Title     = {The $K$-book: An introduction to algebraic $K$-theory},        
    Publisher = {Amer. Math. Soc.},
    Series    = {Grad. Texts Math.},
    Volume    = 145,
    Year      = 2013}
\end{filecontents}
\end{document}

>>>>

%
%-----------------headlines-----------------------------------
\usepackage{amscd, amsmath, amssymb, amsthm, amsfonts, amstext, verbatim, mathtools, xfrac, microtype, nameref, thmtools}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[breaklinks=false,unicode]{hyperref}
\definecolor{DarkPurple}{rgb}{0.40,0.0,0.20}
\hypersetup{colorlinks=true,citecolor=NavyBlue,linkcolor=DarkPurple,urlcolor=NavyBlue}
\usepackage{color} 
\usepackage[capitalize]{cleveref}
\usepackage[matrix,arrow,curve]{xy}
\usepackage{tikz}
\usepackage{enumitem}

@@

\def\LOCAL{\horrocks.files}
%\renewcommand*{\bibfont}{\footnotesize}
%\defbibheading{bibliography}[\refname]{\section*{#1} \markboth{}{}}

@@

The following proposition is the main result of this subsection and also a direct generalization of~\cite[Lemma~3.3]{Tu83}.
\begin{prop} \label{lemma33} For $\Phi=\rA_{\geq 4}, \rD_{\geq 5}, \rE_{6,7,8}$ and $n \geq 1$ the homomorphism $i_n\colon \St^{\leq n}(\Phi, B) \to \St^{\leq n+1}(\Phi, B)$, induced by the natural embedding of generators, is an isomorphism. Consequently, the obvious homomorphism $\St^{\leq 1}(\Phi, B) \to \St(\Phi, B)$ is an isomorphism. \end{prop}
\begin{proof}
 We need to construct a homomorphism $j_n$ which would be the inverse of $i_n$. 
 We start with a homomorphism $\widetilde{j}_n^\Phi \colon F\langle \mathcal{X}^\Phi_{\leq n+1} \rangle \to \St^{\leq n}(\Phi, B)$ defined via
 \[ \widetilde{j}^{\Phi}_n(x_\alpha(at^k)) = \begin{cases} x_\alpha(at^k), & k\leq n; \\
      [x_{\alpha - \beta} (N_{\alpha-\beta, \beta} \cdot at^{k-1}), x_{\beta}(t)], & k = n+1, \end{cases} \]
 where $\beta$ is any root of $\Phi$ forming a sharp angle with $\alpha$.
 A standard argument, cf. \cite[Proposition~1.1]{Re75} or~\cite[Proposition~3.2.2]{RS76}, shows that $\widetilde{j}^\Phi_n$ does not depend on the choice of $\beta$.

@@

\begin{thebibliography}{1000}
\bibitem{Abe83}
 E.~Abe, 
 \emph{\href{https://dx.doi.org/10.1080/00927878308822906} 
 {Whitehead groups of {C}hevalley groups over polynomial rings}},
 Comm. Alg. \textbf{11} (1983), no.~12, 1271--1307.

\bibitem{A13}
 D.~Allcock, 
 \emph{\href{https://dx.doi.org/10.2140/ant.2016.10.1791} 
 {Steinberg groups as amalgams}},
 Alg. Number Th. \textbf{10} (2016), no.~8, 1791--1843.

\bibitem{AF17}
 A.~Asok and J.~Fasel, 
 \emph{\href{https://dx.doi.org/10.1112/topo.12007} 
 {An explicit KO-degree map and applications}},
 J. Top. \textbf{10} (2017), 268--300.

\bibitem{Ba74}
 H.~Bass, 
 \emph{\href{https://dx.doi.org/10.2307/2373586} 
 {Clifford algebras and spinor norms over a commutative ring}},
 Amer. J. Math. \textbf{96} (1974), no.~1, 156--206.

\bibitem{Bou81}
 N.~Bourbaki, 
 \emph{Groupes et algèbres de Lie: Chapitres 4, 5 et 6},
 Masson, 1981.

\bibitem{DS73}
 R.~K.~Dennis and M.~R.~Stein,
 \emph{\href{https://dx.doi.org/10.1007/BFb0073728} 
 {The functor $\K_2$: A survey of computations and problems}},
 Classical Algebraic K-Theory, and Connections with Arithmetic, Springer, 1973, pp.~241--303.

\bibitem{FRS12}
 J.~Fasel, R.~Rao, and R.~Swan,
 \emph{\href{https://dx.doi.org/10.1007/s10240-012-0041-y} 
 {On stably free modules over affine algebras}},
 Publ. Math. IH{\'E}S \textbf{116} (2012), 223--243.

\bibitem{Ho05}
 J.~Hornbostel, 
 \emph{\href{https://dx.doi.org/10.1016/j.top.2004.10.004} 
 {$\mathbb{A}^1$-representability of hermitian K-theory and Witt groups}},
 J. Top. \textbf{44} (2005), no.~3, 661--687.

\bibitem{Ho64}
 G.~Horrocks, 
 \emph{\href{https://dx.doi.org/10.1112/plms/s3-14.4.714} 
 {Projective modules over an extension of a local ring}},
 Proc. London Math. Soc. \textbf{3} (1964), no.~4, 714--718.

\bibitem{Hur77}
 J.~Hurrelbrink, 
 \emph{\href{https://dx.doi.org/10.1007/BF01351716} 
 {Endlich pr\"asentierte arithmetische gruppen und $K_{2}$ {\"u}ber Laurent-polynomringen}},
 Math. Ann. \textbf{225} (1977), no.~2, 123--129.

\bibitem{Ka80}
 M.~Karoubi, 
 \emph{\href{https://dx.doi.org/10.2307/1971147} 
 {Le th{\'e}oreme fondamental de la K-th{\'e}orie hermitienne}},
 Ann. Math. \textbf{112} (1980), no.~2, 259--282.

\bibitem{Lam10}
 T.-Y.~Lam, 
 \emph{Serre's problem on projective modules},
 Springer Science \& Business Media, 2010.

\bibitem{La18}
 A.~Lavrenov, 
 \emph{\href{https://dx.doi.org/10.25537/dm.2018v23.653-675}
 {A local-global principle for symplectic $\K_2$}},
 Doc. Math. \textbf{23} (2018), 653--675.

\bibitem{LS17}
 A.~Lavrenov and S.~Sinchuk,
 \emph{\href{https://arxiv.org/pdf/1606.00272.pdf} 
 {Centrality of odd orthogonal $\K_2$}},
 J. Pure Appl. Alg. \textbf{221} (2017), 1134--1145.

\bibitem{Lo78}
 J.-L.~Loday,
 \emph{\href{https://dx.doi.org/10.1016/0021-8693(78)90025-X}
 {Cohomologie et groupes de Steinberg relatifs}}, 
 J. Alg. \textbf{54} (1978), no.~1, 178--202.

\bibitem{Ma69}
 H.~Matsumoto,
 \emph{\href{http://eudml.org/doc/81843} 
 {Sur les sous-groupes arithm{\'e}tiques des groupes semi-simple d{\'e}ploy{\'e}s}},
 Ann. Sci. ENS \textbf{2} (1969), no.~1, 1--62.

\bibitem{Mo04}
 F.~Morel,
 \emph{\href{https://dx.doi.org/10.1007/s00014-004-0815-z} 
 {Sur les puissances de l'id{\'e}al fondamental de l'anneau de Witt}},
 Comm. Math. Helv. \textbf{79} (2004), no.~4, 689--703.

\bibitem{MR91}
 J.~Morita and U.~Rehmann,
 \emph{\href{https://dx.doi.org/10.1007/BF02571324} 
 {Symplectic $\K_2$ of Laurent polynomials, associated Kac--Moody groups and Witt rings}},
 Math. Z. \textbf{206} (1991), no.~1, 57--66.

\bibitem{Pa89}
 I.~Panin, 
 \emph{\href{http://www.mathnet.ru/links/a46c953dc23ca4b3c44578c283cd59c8/aa27.pdf} 
 {On stabilization for orthogonal and symplectic algebraic K-theory (Russian)}},
 Leningrad Math. J. \textbf{1} (1990), no.~3, 741--754.

\bibitem{Qu76}
 D.~Quillen, 
 \emph{\href{https://dx.doi.org/10.1007/BF01390008} 
 {Projective modules over polynomial rings}},
 Inv. Math. \textbf{36} (1976), no.~1, 167--171.

\bibitem{Re75}
 U.~Rehmann, 
 \emph{\href{http://www.math.uni-bielefeld.de/~rehmann/Publ/praesentation.pdf}
 {Pr{\"a}sentationen von Chevalleygruppen {\"u}ber $k[t]$}}, preprint (1975).

\bibitem{RS76}
 U.~Rehmann and C.~Soul{\'e},
 \emph{\href{https://dx.doi.org/10.1007/BFb0079999} 
 {Finitely presented groups of matrices}}, 
 Algebraic K-Theory, Lect. Notes. Math., vol. 551, Springer, 1976, pp.~164--169.

\bibitem{Sch16}
 M.~Schlichting, 
 \emph{\href{https://dx.doi.org/10.1016/j.jpaa.2016.12.026} 
 {Hermitian K-theory, derived equivalences and Karoubi's fundamental theorem}},
 J. Pure Appl. Alg. \textbf{221} (2017), 1729--1844.

\bibitem{S15}
 S.~Sinchuk, 
 \emph{\href{https://dx.doi.org/10.1016/j.jpaa.2015.08.003}
 {On centrality of $K_2$ for Chevalley groups of type $\mathsf{E}_\ell$}},
 J. Pure Appl. Alg. \textbf{220} (2016), no.~2, 857--875.

\bibitem{St-poly}
 A.~Stavrova, 
 \emph{\href{https://dx.doi.org/10.1017/is013006012jkt232} 
 {Homotopy invariance of non-stable $\K_1$-functors}}, 
 J. K-th. \textbf{13} (2014), no.~2, 199--248.

\bibitem{St-Ded}
 A.~Stavrova, 
 \emph{\href{https://dx.doi.org/10.1515/jgth-2019-0100} 
 {Chevalley groups of polynomial rings over Dedekind domains}}, 
 J. Gr. Th. \textbf{23} (2020), 121--132.

\bibitem{St71}
 M.~R.~Stein, 
 \emph{\href{https://dx.doi.org/10.2307/2373742} 
 {Generators, relations and coverings of Chevalley groups over commutative rings}},
 Amer. J. Math. \textbf{93} (1971), no.~4, 965--1004.

\bibitem{Ste73}
 M.~R.~Stein, 
 \emph{\href{https://dx.doi.org/10.2307/1996696} 
 {Surjective stability in dimension 0 for $\K_2$ and related functors}},
 Trans. Amer. Math. Soc. \textbf{178} (1973), 165--191.

\bibitem{St78}
 M.~R.~Stein, 
 \emph{\href{https://dx.doi.org/10.4099/math1924.4.77} 
 {Stability theorems for $\K_1$, $\K_2$ and related functors modeled on Chevalley groups}},
 Japan J. Math. \textbf{4} (1978), 77--108.

\bibitem{St67}
 R.~Steinberg, J.~Faulkner, and R.~Wilson, 
 \emph{Lectures on Chevalley groups},
 Yale Univ. New Haven, 1967.

\bibitem{Su76}
 A.~Suslin, 
 \emph{\href{http://www.mathnet.ru/links/1ebfa3efeb44dfd494087eaf83a34450/dan40545.pdf} 
 {Projective modules over polynomial rings are free}}, 
 Dokl. Akad. Nauk SSSR \textbf{229} (1976), 1063--1066.

\bibitem{Su77}
 A.~Suslin, 
 \emph{\href{https://dx.doi.org/10.1070/IM1977v011n02ABEH001709} 
 {On the structure of the special linear group over commutative rings}},
 Math. USSR Izv. \textbf{11} (1977), 221--238.

\bibitem{Su82}
 A.~Suslin and V.~Kopeiko, 
 \emph{\href{https://dx.doi.org/10.1007/BF01681481} 
 {Quadratic modules and the orthogonal group over polynomial rings}},
 J. Soviet Math. \textbf{20} (1982), no.~6, 2665--2691.

\bibitem{ST76}
 A.~Suslin and M.~Tulenbaev, 
 \emph{\href{https://dx.doi.org/10.1007/BF01091768} 
 {Stabilization theorem for the Milnor $K_2$-functor}},
 J. Soviet Math. \textbf{17} (1981), no.~2, 1804--1819.

\bibitem{Ta86}
 G.~Taddei, 
 \emph{\href{http://www.ams.org/books/conm/055.2/862660/conm862660.pdf}
 {Normalit\'e des groupes \'el\'ementaires dans les groupes de Chevalley sur un anneau}},
 Applications of algebraic $\K$-theory to algebraic geometry and number theory, Part II (Boulder, Colo., 1983),
 Contemp. Math, vol.~55, 1986, pp.~693--710.

\bibitem{Tu83}
 M.~Tulenbaev, 
 \emph{\href{https://dx.doi.org/10.1070/SM1983v045n01ABEH002591}
 {The Steinberg group of a polynomial ring}},
 Math. USSR Sb. \textbf{45} (1983), 131--144.

\bibitem{Va86}
 L.~Vaserstein, 
 \emph{\href{https://dx.doi.org/10.2748/tmj/1178228489}
 {On normal subgroups of Chevalley groups over commutative rings}},
 Tohoku Math. J. \textbf{38} (1986), 219--230.

\bibitem{V00}
 N.~Vavilov, 
 \emph{\href{http://eudml.org/doc/108535}
 {A third look at weight diagrams}}, 
 Rend. Sem. Mat. Univ. Padova \textbf{104} (2000), 201--250.

\bibitem{VP}
 N.~Vavilov and E.~Plotkin, 
 \emph{\href{https://dx.doi.org/10.1007/BF00047884}
 {Chevalley groups over commutative rings: I. Elementary calculations}},
 Acta Appl. Math. \textbf{45} (1996), 73--113.

\bibitem{VZ18}
 N.~Vavilov and Z.~Zhang, 
 \emph{\href{https://dx.doi.org/10.1017/S0013091519000555}
 {Generation of relative commutator subgroups in Chevalley groups. II}},
 Proc. Edinburgh Math. Soc. \textbf{63} (2020), no.~2, 497--511.

\bibitem{Vo11}
 K.~V{\"o}lkel,
 \emph{\href{http://static.konradvoelkel.de/download/da-voelkel-20110809.pdf}
 {Matsumotos Satz und $\mathbb{A}^1$-Homotopietheorie}},
 Diplomarbeit, Uni. Freiburg.

\bibitem{Kbook}
 C.~A.~Weibel, 
 \emph{The $K$-book: An introduction to algebraic $K$-theory},
 Grad. Texts Math., vol. 145, Amer. Math. Soc., 2013.
\end{thebibliography}

\Addresses
\end{document}
